---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# `segapp`

<!-- badges: start -->
<!-- badges: end -->

`segapp` is an updated version of the [Blood Glucose Monitoring System Surveillance Program](https://www.diabetestechnology.org/seg/)

## Installation

`segapp` is designed to work with [`segtools`](https://mjfrigaard.github.io/segtools/index.html), the utility package for the Surveillance Error Grid calculations and data manipulations.

```{r pkgs, message=FALSE, warning=FALSE}
# install.packages('remotes')
# remotes::install_github("mjfrigaard/segtools", force = TRUE, quiet = TRUE)
library(segtools)
library(segapp)
```

## How it works

`segapp` is a [shiny application built as an R package](https://mastering-shiny.org/scaling-packaging.html), which means it's self-contained and contains, ["*reusable R functions, the documentation that describes how to use them, and sample data.*"](https://r-pkgs.org/).

## Running the application 

To run the development version of the application, install and load segapp and use `run_dev()`:

```r
install.packages('remotes')
# ensure current version
remotes::install_github("mjfrigaard/segapp", force = TRUE, quiet = TRUE)
library(segapp)
run_dev()
```

The production version of the application can be deployed by running `run_app()`, which is contained in the `app.R` file.





